---
title: "LA_8"
author: "Adam Hayes, Richard Park, Jasmine Sanchez, Erin Omyer"
date: "3/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(data.table)
```



##What factors lead a YouTube channel to be successful?
This is important because there are so many YouTube channels out there, and for people trying to create their own channel, and for YouTube itself, it is interesting to know what influences certain channels to become successful.  YouTube may want to help certain channels get off the ground if they display certain characteristics that have translated to success.  Also, knowing which characteristics correlate with success will give users a better ground to start on when creating their own YouTube channel.

###Our Dataset
Our dataset contains the top 5000 rated YouTube channels by Socialblade.

https://www.kaggle.com/mdhrumil/top-5000-youtube-channels-data-from-socialblade

vars:
Rank = the Socialblade rankings of the YouTube channel.
Grade =  the grade of the YouTube channel as conferred by Socialblade.
Channel name = The name of the YouTube channel.
Uploads = Total number of videos uploaded by the YouTube channel.
Subscribers = Total number of subscribers of the YouTube channel.
Views = Total number of views of all the video content by the YouTube channel.
Uploaded videos = Total number number of uploaded videos by the Youtube channel. 


###Domain Expert
Our domain expert is the CEO of YouTube, and he wants to know what factors are leading to certain YouTube channels becoming more successful based on Socialblade's rankings.  It is interesting to him what a major blogger company like Socialblade finds important in certain YouTube channels because he believes it influences the way users look at and evaluate channels.  He wants to know which channels he should focus his sponsorships towards in order to increase YouTube's overall success.  



###Adam's Findings

```{r}
dataAdam <- fread("data.csv", na.strings = c("--"))%>%
  rename(Uploads = "Video Uploads", Views = "Video views")


data2 <- dataAdam %>%
  separate(Rank, into = c("rank","word"), sep = -2)%>%
  select(-word)

data2$Uploads <- as.numeric(data2$Uploads)
data2$Views <- as.numeric(data2$Views)
data2$Subscribers <- as.numeric(data2$Subscribers)
data2$rank <- as.numeric(data2$rank)

data3 <- data2 %>%
  mutate(rate = Subscribers / Uploads)



ggplot(data = data3, mapping = aes(x = rate, y = Uploads ))+
  geom_point(position = "jitter")+
  xlim(0,100)+
  labs(title = "Rate of Subscribers:Uploads vs. # of Uploads")



ggplot(data = data3, mapping = aes(x = rank, y = Uploads))+
  geom_point()+
  ylim(0,100000)+
  labs(title = "Channel Rank vs. # of Uploads")
```

####Comments
I explored how the number of uploads a channel has effects the overall success of the channel.  In the first graph I created a new rate variable that represented the number of subscribers per upload, and when I compared that with how many uploads each channel has I found that the rate tends to be much higher with less uploads, and much lower when a channel has more uploads.  In the second graph, I compared the channel rank with it's number of uploads, and found that the number of uploads does not correlate at all with a channels rank, as some channels with very good rankings have very little uploads while others with good rankings have high uploads.


###Erin's Findings

```{r}
data <- read_csv("data.csv")
data1 <- data %>% unite("Rank Grade", into = c("Rank","Grade"),sep = "-")
data1 <- data %>% rename(VideoUploads = "Video Uploads", VideoViews = "Video views") 

data1$VideoUploads <- as.numeric(data1$VideoUploads)
data1$Subscribers <- as.numeric(data1$Subscribers)
data1$VideoViews <- as.numeric(data1$VideoViews)

newData <- data1 %>%
  unite("Rank Grade", into = c("Rank","Grade"), sep = "-") %>%
  mutate(SubscriberViews_Rate = (Subscribers/VideoViews)) 

ggplot(data = newData, mapping = aes(x = SubscriberViews_Rate, y = VideoViews)) + geom_point() + geom_smooth(position = "jitter") +
  xlim(0,0.15) +
  ylim(0,40000000000) +
  labs(title = "Rate of Video Views for # of Subscribers")  


```

####Comments
From the data graphed, it is comparing the Subscribers Viewer rate (Subscribers/VideoViews) to the number of Video Views they receive. In the graph displayed, the peak of the Subscribers Viewer rate is when the content creator was just beginning. When you start making videos, you begin with zero and then increase drastically, because you never had subscribers before. In my data, the values were concentrated in the beginning, so I had to make use of focusing the x values from 0 to 0.15 and the y values from 0 to 400000000. As well, the points on the graph were centralized to the 0 Subscriber Rate, so I placed "position = "jitter"" to ensure variance and better visualization of the plot. 

### Richard's Findings

```{r}
dataRichard <- read.csv("data.csv", na.strings = c("--"))
dataRichard1 <- na.omit(dataRichard)
dataYoutube <- dataRichard1 %>%
  rename(UploadedVideos = "Video.Uploads", Views = "Video.views") %>%
  separate(Rank, into = c("rank","word"), sep = -2)%>%
  select(-word)
  
dataYoutube$UploadedVideos <- as.numeric(dataYoutube$UploadedVideos)
dataYoutube$Views <- as.numeric(dataYoutube$Views)
dataYoutube$Subscribers <- as.numeric(dataYoutube$Subscribers)
dataYoutube$rank <- as.numeric(dataYoutube$rank)

dataYoutube1 <- dataYoutube %>%
  mutate(RankBasedOnSubscriberRate = (rank/Subscribers))
  
 ggplot(data = dataYoutube1, mapping = aes(x = rank, y = Subscribers))+ 
   geom_point(position = "jitter")+
   xlim(0,1000)+
   ylim(0,5000)+
   geom_smooth()
   labs(title = "Rank based on # of Uploaded videos")

```

####Comments
As depicted from the graph above, the top 1000 youtube channels (based on rank) were being compared to the number of subscribers they have. The graph depicts a highly scattered output which shows that there is no significant effect of the number of subscribers on a Youtube channels' rank (based on socialblade's rankings). I also utilized "position" = "jitter" to help with visualiztion of the plots on the graph.


###Overall Summary Of Group Work
The group members overall contributed equally to the team project. Erin created a graph to show the visual relationship between the Subscriber Viewer rate and the number of views on a video for the youtuber creators. She discovered that there is a minimal correlation between the rate and the views per video, but a correlation in the beginning. My implementing bounds on her graph, it allows for a 'zoomed' in outlook on the relationships. We are able to see that the rate of Subscriber views is at the highest in the beginning, when youtubers are just starting their creations on youtube. So, inevitably, the rate will be higher. 